Brownian Dynein Model

### 2015-09-29 latex/derivation.tex
changes from our meeting

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

@@

\begin{align}
  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
\end{align}

We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = ab - \sqrt{1-a^2}\sqrt{1-b^2}$$ and $$\sin\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = \sqrt{1-a^2}b+a\sqrt{1-b^2}$$ to simplify our expressions:

>>>>

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

@@

\begin{align}
  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
\end{align}

We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:
